\documentclass[a4paper,10pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[margin=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Adjust list spacing
\setlist[itemize]{noitemsep, topsep=0pt, left=1em}

% Resume starts
\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\Huge \textbf{Samarth Singh Rawat}} \\
    \vspace{3pt}
    \href{mailto:samarthrawat18@email.com}{samarthrawat18@email.com} \,|\, +91 8984100922 \,|\, DGM-2 201, TATA Steel Meramandali Colony, Meramandali, Narendrapur, Odisha - 759121, India \\
    \href{https://github.com/gentlewind-alt}{GitHub}: \,|\, 
    \href{https://www.linkedin.com/in/samarth-rawat}{LinkedIn}
\end{center}

% ---------- SUMMARY ----------
\section*{Summary}
Applied AI developer and B.Tech IT student at KIIT Bhubaneswar, specializing in interactive systems, behavioral architectures, and AI-enhanced user experiences. Experienced in integrating embedded systems, real-time interfaces, and intelligent workflow automation into cohesive, product-oriented applications that merge machine learning, IoT, and scalable web solutions.

% ---------- EDUCATION ----------
\section*{Education}
\textbf{Kalinga Institute of Industrial Technology (KIIT)}, Bhubaneswar, Odisha \\
Bachelor of Technology in Information Technology \hfill 2026 \\
8th Semester CGPA: 8.24

\vspace{4pt}
\textbf{Lal Bahadur Shastri Public School}, Kota \\
12th Grade, CBSE \hfill 2022 \\
Percentage: 79.4\%

\vspace{4pt}
\textbf{GMR DAV Varalakshmi Public School}, Dhenkanal \\
10th Grade, CBSE \hfill 2020 \\
Percentage: 90\%

% ---------- FIELDS OF INTEREST ----------
\section*{Fields of Interest}
LLMs, Artificial Intelligence, Fine tuning, Deep Learning, Agentic AI, Data Visualization, Machine Learning, IoT Systems, Embedded Systems, Human-Computer Interaction, Data Analysis, Web Designing

% ---------- TECHNICAL SKILLS ----------
\section*{Technical Skills}
\textbf{Programming Languages:} Python, Java, C, HTML/CSS \\
\textbf{Frameworks/Libraries:} TensorFlow, Scikit-learn, NumPy, Pandas, Matplotlib \\
\textbf{Tools:} Git, Microsoft Office, Power BI, Arduino, \LaTeX, VS Code \\
\textbf{Databases:} MySQL \\
\textbf{Platforms:} ESP32, Spotify API

% ---------- PROJECTS ----------
\section*{Projects / Open-Source}

\textbf{Critic-OS (Completed)}:
\textit{Python (Flask), Groq (Llama-3.3), HuggingFace, Redis, Spotify API, Last.fm API, Vercel}
\begin{itemize}
    \item Developed an AI-driven web application that generates real-time, satirical music critiques using Groq (Llama-3.3) and 6 distinct AI personas (e.g., Gordon Ramsay, Cyberpunk Hacker).
    \item Engineered a parallel enrichment engine that integrates Spotify, Last.fm, and LRC\_LIB APIs with HuggingFace emotion classification to analyze user playlists in under 6 seconds.
    \item Optimized for production using Vercel Serverless and Redis-backed session management to ensure high-speed performance and efficient memory usage.
\end{itemize}

\vspace{8pt}
\textbf{Movie Recommendation System (Completed)}:
\textit{Python, Scikit-learn, NumPy, HTML}  
\begin{itemize}
    \item Built a collaborative filtering engine to generate personalized movie suggestions.
    \item Processed large datasets and designed a simple web UI for user input and recommendations.
\end{itemize}

\textbf{IoT Smart Alarm Clock (Completed)}:
\textit{ESP32-C3, C++, LittleFS, I2C/SPI, FreeRTOS, Python (Asset Packing)}  
\begin{itemize}
    \item \textbf{Memory-Constrained Architecture}: Engineered a custom \texttt{.bin} streaming animation engine to bypass ESP32-C3 RAM limitations, enabling high-quality animations via LittleFS frame-streaming with 16-byte header verification.
    \item \textbf{Resource Optimization}: Implemented a multi-tier throttling strategy (I2C capping, sensor polling reduction with median filtering, and UI string caching), reducing CPU overhead by 40\% and enhancing system stability.
    \item \textbf{Modular Firmware Design}: Developed a feature-toggle architecture that reduced BSS memory allocation by 65\%, ensuring compatibility with WiFi/BT stacks while maintaining a responsive, interrupt-driven multi-page menu system.
    \item \textbf{System Reliability}: Integrated a heterogeneous sensor suite (PIR, Ultrasonic, IMU) for gesture control and motion wake, synchronized with a dual-source (NTP + Hardware RTC) timekeeping system for offline resilience.
\end{itemize}

\textbf{ISL Hand Gesture Recognition Using Random Forest (Completed)}:
\textit{Python, Scikit-learn, NumPy, Pandas}  
\begin{itemize}
    \item Processed ISL hand gesture datasets in CSV format with landmark and movement data.
    \item Trained a Random Forest model to classify Indian Sign Language gestures accurately.
\end{itemize}

% ---------- STRENGTHS ----------
\section*{Strengths}
\begin{itemize}
    \item Systems-oriented embedded developer experienced in modular ESP32 architecture, real-time interaction systems, and hardware-software integration.
    \item Strong problem-solving and systems-thinking skills with focus on scalable, maintainable, and extensible design patterns.
    \item Experienced in integrating sensors, displays, RTC modules, animation systems, and input handling into cohesive embedded applications.
    \item Rapid prototyping and iterative development capability with practical debugging experience across complex firmware and hardware interactions.
    \item Cross-domain technical exposure spanning embedded systems, UI/UX interaction design, simulation workflows, and AI-assisted development tools.
\end{itemize}

% ---------- HOBBIES ----------
\section*{Hobbies}
Reading books, Watching movies, Learning new things, Building and innovating, Listening to stories and podcasts
\end{document}
